---
title: "Salad Bar Study: Rurality and Fruit and Vegetable Paper (Jepson)"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
header-includes:
- \usepackage{fullpage}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{float}
- \usepackage{placeins}
- \usepackage{caption}
- \usepackage{mathtools}
# - \usepackage{multirow}
- \usepackage{amssymb}
- \usepackage{amsmath}
- \usepackage{bigstrut}
- \usepackage{geometry}
# - \usepackage{pdflscape}
- \setlength{\parskip}{1em}
geometry: margin=1.3cm
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(comment = FALSE), echo = TRUE, fig.width=6, fig.height=4, fig.path='figs/', fig.pos='H', echo=FALSE, cache = FALSE, warning=FALSE, message=FALSE, comment = NA)
```

<!-- load startup file and any extra packages -->
```{r load, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(stats)
library(haven)
library(psycho)
library(reshape2)
library(gtsummary)
theme_gtsummary_compact()

library(car)
library(emmeans)
library(lubridate)
library(GLMMadaptive)

library(lme4)
library(lmerTest)

library(ggplot2)
library(ggpubr)
library(ggsignif)


source('functions.R')
```

```{r load_scripts, echo=FALSE, results='asis'}
source('setup.R')
source('rurality_analyses.R')
source('rurality_tables.R')
```

\clearpage

# Demographic Characteristics

```{r demo_tab, echo=FALSE, results='asis'}
  as_kable_extra(overall_table_rural2, caption = 'Demographic Characteristics', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage

## Gender
```{r demo_gender, echo=FALSE}
gender_chi
```

## age
```{r demo_age, echo=FALSE}
age_ttest
```

## grade
```{r demo_grade, echo=FALSE}
grade_ttest
```

## race/ethnicity
```{r demo_race, echo=FALSE}
raceethnicity_chi

xtabs(~rurality2 + race_ethnicity, data = salad_bar_dat_use)
```

## free-reduced lunch
```{r demo_frl, echo=FALSE}
frl_chi

xtabs(~rurality2 + paid_free_reduced, data = salad_bar_dat_use)
```

## fruit/veg selected
```{r demo_fv_select, echo=FALSE}
fv_selected_chi
```

\FloatBarrier
\clearpage

## fruit/veg amount selected
```{r demo_fv_g_select, echo=FALSE}
fv_pre_anova
fv_pre_emmeans
```

## fruit/veg consumed
```{r demo_fv_consumed, echo=FALSE}
fv_consumed_anova
fv_consumed_emmeans
```

## fruit/veg waste
```{r demo_fv_waste, echo=FALSE}
fv_waste_anova
fv_waste_emmeans
```

## fruit/veg waste proportion
```{r demo_fv_prop_waste, echo=FALSE}
fv_prop_waste_anova
fv_prop_waste_emmeans
```

\FloatBarrier
\clearpage

# Rurality Models - 2 category

## Fruit/Vegetable Self-Served

```{r fv_pre_plot2, echo=FALSE, include = TRUE}
hist(salad_bar_dat_use[['fv_pre']])
```

\FloatBarrier

-mean and sd for participants that selected F/V

```{r fv_pre_mean2, echo=FALSE}
mean(salad_bar_dat_use[salad_bar_dat_use[['fv_pre']] > 0, 'fv_pre'], na.rm = TRUE)

sd(salad_bar_dat_use[salad_bar_dat_use[['fv_pre']] > 0, 'fv_pre'], na.rm = TRUE)
```

\FloatBarrier


### Overall model

```{r fv_pre_mod2, echo=FALSE}
fv_served_sum2
```

\FloatBarrier

#### irr

```{r fv_pre_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_served_sum2$coef_table[ ,1]), nrow = 9, round = 3)
```

\FloatBarrier

#### or

```{r fv_pre_or2, echo=FALSE}
as.matrix(exp(fv_served_sum2$coef_table_zi[ ,1]), nrow = 9, round = 3)
```

\FloatBarrier
\clearpage

<!-- ### Rurality x School Level -->

<!-- ```{r fv_pre_int_mod2, echo=FALSE} -->
<!-- fv_served_int_sum2 -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### irr -->

<!-- ```{r fv_pre_int_irr2, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_served_int_sum2$coef_table[ ,1]), nrow = 16) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### or -->

<!-- ```{r fv_pre_int_or2, echo=FALSE} -->
<!-- as.matrix(exp(fv_served_int_sum2$coef_table_zi[ ,1]), nrow = 16) -->
<!-- ``` -->

<!-- \FloatBarrier -->

### Rurality x Gender

```{r fv_pre_gender_mod2, echo=FALSE}
fv_served_gender_sum2
```

\FloatBarrier

#### Zero model Marginal means
```{r fv_pre_gender_fix_emt2, echo=FALSE, asis = TRUE}
fv_served_gender_fixed_emt2
```

\FloatBarrier

#### irr

```{r fv_pre_gender_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_served_gender_sum2$coef_table[ ,1]), nrow = 11)
```

\FloatBarrier

#### or

```{r fv_pre_gender_or2, echo=FALSE}
as.matrix(exp(fv_served_gender_sum2$coef_table_zi[ ,1]), nrow = 11)
```

\FloatBarrier

### Rurality x Eating Duration

```{r fv_pre_tte_mod2, echo=FALSE}
fv_served_tte_sum2
```

\FloatBarrier

#### irr

```{r fv_pre_tte_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_served_tte_sum2$coef_table[ ,1]), nrow = 11)
```

\FloatBarrier

#### Zero model Marginal Slopes
```{r fv_pre_tte_zi_emt2, echo=FALSE, asis = TRUE}
fv_served_tte_zi_emt2
```

\FloatBarrier

#### or

```{r fv_pre_tte_or2, echo=FALSE}
as.matrix(exp(fv_served_tte_sum2$coef_table_zi[ ,1]), nrow = 11)
```

\FloatBarrier
\clearpage

## Fruit/Vegetable Consumed

```{r fv_consumed_plot2, echo=FALSE, include = TRUE}
hist(salad_bar_dat_use[salad_bar_dat_use[['fv_selected']] == 'Y', 'fv_consumed'])
```

\FloatBarrier

-mean and sd for participants that selected F/V and consumed > 0 g F/V

```{r fv_consumed_mean2, echo=FALSE, results='asis'}
mean(salad_bar_dat_use[salad_bar_dat_use[['fv_consumed']] > 0, 'fv_consumed'], na.rm = TRUE)
sd(salad_bar_dat_use[salad_bar_dat_use[['fv_consumed']] > 0, 'fv_consumed'], na.rm = TRUE)
```


\FloatBarrier

### Overall model

```{r fv_consumed_mod2, echo=FALSE}
fv_consumed_sum2
```

\FloatBarrier

#### irr

```{r fv_consumed_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_consumed_sum2$coef_table[ ,1]), nrow = 10)
```

\FloatBarrier

#### or

```{r fv_consumed_or2, echo=FALSE}
as.matrix(exp(fv_consumed_sum2$coef_table_zi[ ,1]), nrow = 10)
```

\FloatBarrier

<!-- ### Rurality x School Level -->

<!-- ```{r fv_consumed_int_mod2, echo=FALSE} -->
<!-- fv_consumed_int_sum2 -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### irr -->

<!-- ```{r fv_consumed_int_irr2, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_consumed_int_sum2$coef_table[ ,1]), nrow = 16) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### or -->

<!-- ```{r fv_consumed_int_or2, echo=FALSE} -->
<!-- as.matrix(exp(fv_consumed_int_sum2$coef_table_zi[ ,1]), nrow = 16) -->
<!-- ``` -->

<!-- \FloatBarrier -->

### Rurality x Gender

```{r fv_consumed_gender_mod2, echo=FALSE}
fv_consumed_gender_sum2
```

\FloatBarrier

#### irr

```{r fv_consumed_gender_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_consumed_gender_sum2$coef_table[ ,1]), nrow = 12)
```

\FloatBarrier

#### or

```{r fv_consumed_gender_or2, echo=FALSE}
as.matrix(exp(fv_consumed_gender_sum2$coef_table_zi[ ,1]), nrow = 12)
```

\FloatBarrier

### Rurality x Eating Duration

```{r fv_consumed_tte_mod2, echo=FALSE}
fv_consumed_tte_sum2
```

\FloatBarrier

#### irr

```{r fv_consumed_tte_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_consumed_tte_sum2$coef_table[ ,1]), nrow = 13)
```

\FloatBarrier

#### Zero model Marginal Slopes
```{r fv_consumed_tte_zi_emt2, echo=FALSE, asis = TRUE}
fv_consumed_tte_zi_emt2
```

\FloatBarrier

#### or

```{r fv_consumed_tte_or2, echo=FALSE}
as.matrix(exp(fv_consumed_tte_sum2$coef_table_zi[ ,1]), nrow = 13)
```

\FloatBarrier
\clearpage

## Fruit/Vegetable Propor2tion Waste



```{r fv_prop_waste_plot2, echo=FALSE, include = TRUE}
hist(salad_bar_dat_use[salad_bar_dat_use[['fv_selected']] == 'Y', 'fv_prop_waste'], main = 'Histogram of Percent Fruits/Vegetables Waste, %', xlab = 'Fruit/Vegetables, %')
```

\FloatBarrier

-mean and sd for participants that selected F/V and consumed > 0 g F/V

```{r fv_prop_waste_mean2, echo=FALSE}
mean(salad_bar_dat_use[salad_bar_dat_use$fv_prop_waste < 100 & salad_bar_dat_use$fv_prop_waste > 0 & salad_bar_dat_use$fv_selected == 'Y', 'fv_prop_waste'])

sd(salad_bar_dat_use[salad_bar_dat_use$fv_prop_waste < 100 & salad_bar_dat_use$fv_prop_waste > 0 & salad_bar_dat_use$fv_selected == 'Y', 'fv_prop_waste'])
```

\FloatBarrier

### Overall model

```{r fv_prop_waste_mod2, echo=FALSE}
fv_prop_waste_sum2
```

\FloatBarrier

#### irr

```{r fv_prop_waste_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_prop_waste_sum2$coef_table[ ,1]), nrow = 9)
```

\FloatBarrier

#### or

```{r fv_prop_waste_or2, echo=FALSE}
as.matrix(exp(fv_prop_waste_sum2$coef_table_zi[ ,1]), nrow = 9)
```

\FloatBarrier
\clearpage

<!-- ### Rurality x School Level -->

<!-- ```{r fv_prop_waste_int_mod2, echo=FALSE} -->
<!-- fv_prop_waste_int_sum2 -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### irr -->

<!-- ```{r fv_prop_waste_int_irr2, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_prop_waste_int_sum2$coef_table[ ,1]), nrow = 9) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### or -->

<!-- ```{r fv_prop_waste_int_or2, echo=FALSE} -->
<!-- as.matrix(exp(fv_prop_waste_int_sum2$coef_table_zi[ ,1]), nrow = 9) -->
<!-- ``` -->

<!-- \FloatBarrier -->

### Rurality x Gender

```{r fv_prop_waste_gender_mod2, echo=FALSE}
fv_prop_waste_gender_sum2
```

\FloatBarrier

#### irr

```{r fv_prop_waste_gender_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_prop_waste_gender_sum2$coef_table[ ,1]), nrow = 9)
```

\FloatBarrier

#### or

```{r fv_prop_waste_gender_or2, echo=FALSE}
as.matrix(exp(fv_prop_waste_gender_sum2$coef_table_zi[ ,1]), nrow = 9)
```

\FloatBarrier
\clearpage

### Rurality x Eating Duration

```{r fv_prop_waste_tte_mod2, echo=FALSE}
fv_prop_waste_tte_sum2
```

\FloatBarrier

#### Count model Marginal Slopes
```{r fv_prop_waste_tte_fixed_emm2, echo=FALSE, asis = TRUE}
fv_prop_waste_tte_fixed_emm2
```

\FloatBarrier

#### irr

```{r fv_prop_waste_tte_irr2, echo=FALSE, asis = TRUE}
as.matrix(exp(fv_prop_waste_tte_sum2$coef_table[ ,1]), nrow = 13)
```

\FloatBarrier

#### or

```{r fv_prop_waste_tte_or2, echo=FALSE}
as.matrix(exp(fv_prop_waste_tte_sum2$coef_table_zi[ ,1]), nrow = 13)
```

\FloatBarrier
\clearpage

<!-- # Rurality Models - 3 category -->

<!-- ## Demographic Characteristics -->

<!-- ```{r demo_tab_3cat, echo=FALSE, results='asis'} -->
<!--   as_kable_extra(overall_table_rural, caption = 'Demographic Characteristics', format = "latex", booktabs = TRUE, longtable = FALSE) %>% -->
<!--   kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE) -->
<!-- ``` -->

<!-- \FloatBarrier -->
<!-- \clearpage -->

<!-- ## Fruit/Vegetable Self-Served -->

<!-- ```{r fv_pre_plot, echo=FALSE, include = TRUE} -->
<!-- hist(salad_bar_dat_use[['fv_pre']]) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- -mean and sd for participants that selected F/V -->

<!-- ```{r fv_pre_mean, echo=FALSE} -->
<!-- mean(salad_bar_dat_use[salad_bar_dat_use[['fv_pre']] > 0, 'fv_pre'], na.rm = TRUE) -->

<!-- sd(salad_bar_dat_use[salad_bar_dat_use[['fv_pre']] > 0, 'fv_pre'], na.rm = TRUE) -->
<!-- ``` -->

<!-- \FloatBarrier -->


<!-- ### Overall model -->

<!-- ```{r fv_pre_mod, echo=FALSE} -->
<!-- fv_served_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_pre_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_served_sum$coef_table[ ,1]), nrow = 10) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_pre_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_served_sum$coef_table_zi[ ,1]), nrow = 10) -->
<!-- ``` -->

<!-- \FloatBarrier -->
<!-- \clearpage -->

<!-- ### Rurality x School Level -->

<!-- ```{r fv_pre_int_mod, echo=FALSE} -->
<!-- fv_served_int_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_pre_int_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_served_int_sum$coef_table[ ,1]), nrow = 16) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_pre_int_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_served_int_sum$coef_table_zi[ ,1]), nrow = 16) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- ### Rurality x Gender -->

<!-- ```{r fv_pre_gender_mod, echo=FALSE} -->
<!-- fv_served_gender_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### Count Model Marginal Means -->
<!-- ```{r fv_pre_gender_fix_emm, echo=FALSE, asis = TRUE} -->
<!-- fv_served_gender_fixed_emm -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_pre_gender_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_served_gender_sum$coef_table[ ,1]), nrow = 12) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_pre_gender_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_served_gender_sum$coef_table_zi[ ,1]), nrow = 12) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- ### Rurality x Eating Duration -->

<!-- ```{r fv_pre_tte_mod, echo=FALSE} -->
<!-- fv_served_tte_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_pre_tte_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_served_tte_sum$coef_table[ ,1]), nrow = 13) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### Zero Model Marginal Slopes -->
<!-- ```{r fv_pre_tte_zi_emt, echo=FALSE, asis = TRUE} -->
<!-- fv_served_tte_zi_emt -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_pre_tte_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_served_tte_sum$coef_table_zi[ ,1]), nrow = 13) -->
<!-- ``` -->

<!-- \FloatBarrier -->
<!-- \clearpage -->

<!-- ## Fruit/Vegetable Consumed -->

<!-- ```{r fv_consumed_plot, echo=FALSE, include = TRUE} -->
<!-- hist(salad_bar_dat_use[salad_bar_dat_use[['fv_selected']] == 'Y', 'fv_consumed']) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- -mean and sd for participants that selected F/V and consumed > 0 g F/V -->

<!-- ```{r fv_consumed_mean, echo=FALSE, results='asis'} -->
<!-- mean(salad_bar_dat_use[salad_bar_dat_use[['fv_consumed']] > 0, 'fv_consumed'], na.rm = TRUE) -->
<!-- sd(salad_bar_dat_use[salad_bar_dat_use[['fv_consumed']] > 0, 'fv_consumed'], na.rm = TRUE) -->
<!-- ``` -->


<!-- \FloatBarrier -->

<!-- ### Overall Model -->

<!-- ```{r fv_consumed_mod, echo=FALSE} -->
<!-- fv_consumed_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_consumed_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_consumed_sum$coef_table[ ,1]), nrow = 10) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_consumed_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_consumed_sum$coef_table_zi[ ,1]), nrow = 10) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- ### Rurality x School Level -->

<!-- ```{r fv_consumed_int_mod, echo=FALSE} -->
<!-- fv_consumed_int_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_consumed_int_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_consumed_int_sum$coef_table[ ,1]), nrow = 16) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_consumed_int_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_consumed_int_sum$coef_table_zi[ ,1]), nrow = 16) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- ### Rurality x Gender -->

<!-- ```{r fv_consumed_gender_mod, echo=FALSE} -->
<!-- fv_consumed_gender_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_consumed_gender_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_consumed_gender_sum$coef_table[ ,1]), nrow = 12) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_consumed_gender_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_consumed_gender_sum$coef_table_zi[ ,1]), nrow = 12) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- ### Rurality x Eating Duration -->

<!-- ```{r fv_consumed_tte_mod, echo=FALSE} -->
<!-- fv_consumed_tte_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_consumed_tte_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_consumed_tte_sum$coef_table[ ,1]), nrow = 13) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### Zero Model Marginal Slopes -->
<!-- ```{r fv_consumed_tte_zi_emt, echo=FALSE, asis = TRUE} -->
<!-- fv_consumed_tte_zi_emt -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_consumed_tte_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_consumed_tte_sum$coef_table_zi[ ,1]), nrow = 13) -->
<!-- ``` -->

<!-- \FloatBarrier -->
<!-- \clearpage -->

<!-- ## Fruit/Vegetable Proportion Waste -->



<!-- ```{r fv_prop_waste_plot, echo=FALSE, include = TRUE} -->
<!-- hist(salad_bar_dat_use[salad_bar_dat_use[['fv_selected']] == 'Y', 'fv_prop_waste'], main = 'Histogram of Percent Fruits/Vegetables Waste, %', xlab = 'Fruit/Vegetables, %') -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- -mean and sd for participants that selected F/V and consumed > 0 g F/V -->

<!-- ```{r fv_prop_waste_mean, echo=FALSE} -->
<!-- mean(salad_bar_dat_use[salad_bar_dat_use$fv_prop_waste < 100 & salad_bar_dat_use$fv_prop_waste > 0 & salad_bar_dat_use$fv_selected == 'Y', 'fv_prop_waste']) -->

<!-- sd(salad_bar_dat_use[salad_bar_dat_use$fv_prop_waste < 100 & salad_bar_dat_use$fv_prop_waste > 0 & salad_bar_dat_use$fv_selected == 'Y', 'fv_prop_waste']) -->
<!-- ``` -->

<!-- \FloatBarrier -->
<!-- ### Interaction Model -->

<!-- ```{r fv_prop_waste_int_mod, echo=FALSE} -->
<!-- fv_prop_waste_int_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_prop_waste_int_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_prop_waste_int_sum$coef_table[ ,1]), nrow = 9) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_prop_waste_int_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_prop_waste_int_sum$coef_table_zi[ ,1]), nrow = 9) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- ### Overall Model -->

<!-- ```{r fv_prop_waste_mod, echo=FALSE} -->
<!-- fv_prop_waste_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_prop_waste_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_prop_waste_sum$coef_table[ ,1]), nrow = 9) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_prop_waste_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_prop_waste_sum$coef_table_zi[ ,1]), nrow = 9) -->
<!-- ``` -->

<!-- \FloatBarrier -->
<!-- \clearpage -->

<!-- ### Rurality x Gender -->

<!-- ```{r fv_prop_waste_gender_mod, echo=FALSE} -->
<!-- fv_prop_waste_gender_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_prop_waste_gender_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_prop_waste_gender_sum$coef_table[ ,1]), nrow = 9) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_prop_waste_gender_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_prop_waste_gender_sum$coef_table_zi[ ,1]), nrow = 9) -->
<!-- ``` -->

<!-- \FloatBarrier -->
<!-- \clearpage -->

<!-- ### Rurality x Eating Duration -->

<!-- ```{r fv_prop_waste_tte_mod, echo=FALSE} -->
<!-- fv_prop_waste_tte_sum -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### Count Model Marginal Slopes -->
<!-- ```{r fv_prop_waste_tte_fixed_emm, echo=FALSE, asis = TRUE} -->
<!-- fv_prop_waste_tte_fixed_emm -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### IRR -->

<!-- ```{r fv_prop_waste_tte_irr, echo=FALSE, asis = TRUE} -->
<!-- as.matrix(exp(fv_prop_waste_tte_sum$coef_table[ ,1]), nrow = 13) -->
<!-- ``` -->

<!-- \FloatBarrier -->

<!-- #### OR -->

<!-- ```{r fv_prop_waste_tte_or, echo=FALSE} -->
<!-- as.matrix(exp(fv_prop_waste_tte_sum$coef_table_zi[ ,1]), nrow = 13) -->
<!-- ``` -->

<!-- \FloatBarrier -->
<!-- \clearpage -->

