---
title: "Salad Bar Study: Christina - Time to Eat and Fruit and Vegetable Intake"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
header-includes:
- \usepackage{fullpage}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{float}
- \usepackage{placeins}
- \usepackage{caption}
- \usepackage{mathtools}
# - \usepackage{multirow}
- \usepackage{amssymb}
- \usepackage{amsmath}
- \usepackage{bigstrut}
- \usepackage{geometry}
# - \usepackage{pdflscape}
- \setlength{\parskip}{1em}
geometry: margin=1.3cm
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(comment = FALSE), echo = TRUE, fig.width=6, fig.height=4, fig.path='figs/', fig.pos='H', echo=FALSE, cache = FALSE, warning=FALSE, message=FALSE, comment = NA)
```

<!-- load startup file and any extra packages -->
```{r load, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(stats)
library(haven)
library(lubridate)
library(GLMMadaptive)
library(car)
library(emmeans)
library(ggplot2)

library(gtsummary)
theme_gtsummary_compact()

```

```{r load_scripts, echo=FALSE, results='asis'}
source('functions.R')
source('setup.R')
source('tte_analyses.R')
source('tte_tables.R')
```

\clearpage

# Demographic Characteristics
*note - restricted to:
  - pre (selected) > post (waste)
  - time to eat is not NA
  - pre (selected) is not NA
  - post (waste) is not NA
  - missing data for any covariates used in models (age not included in models)
\
\FloatBarrier
```{r demo_tab, echo=FALSE, results='asis'}
  as_kable_extra(overall_table, caption = 'Demographic Characteristics and Variables of Interest', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\
*intake data means and standard deviations restricted to those who selected F/V. Means for consumed restricted to those with FV consumption > 0 is in text with that model.

\FloatBarrier
\clearpage

## Follow-up Tests by School Type

\
\FloatBarrier

### gender
```{r demo_gender_schooltype, echo=FALSE}
gender_chi
```

### age
```{r demo_age_schooltype, echo=FALSE}
age_anova
age_emmeans$contrasts
```

### race/ethnicity
```{r demo_raceethnicity_schooltype, echo=FALSE}
raceethnicity_chi
```

### free-reduced lunch
```{r demo_frl_schooltype, echo=FALSE}
frl_chi
```

### fruit/veg selected
```{r demo_fv_select_schooltype, echo=FALSE}
fv_selected_chi
```

### fruit/veg amount selected
```{r demo_fv_g_select_schooltype, echo=FALSE}
fv_pre_anova
fv_pre_emmeans$contrasts
```

### fruit/veg consumed
```{r demo_fv_consumed_schooltype, echo=FALSE}
fv_consumed_anova
fv_consumed_emmeans$contrasts
```

### fruit/veg waste
```{r demo_fv_waste_schooltype, echo=FALSE}
fv_post_anova
fv_post_emmeans$contrasts
```

### fruit/veg waste proportion
*restricted to selected only
\
\FloatBarrier
```{r demo_fv_prop_waste_schooltype, echo=FALSE}
fv_prop_waste_anova
fv_prop_waste_emmeans$contrasts
```

\FloatBarrier
\clearpage

# Association between TTE and Lunch Duration

```{r tte_lunch_cor, echo=FALSE}
cor.test(salad_bar_dat_use[['time_to_eat']], salad_bar_dat_use[['lunch_dur']], na.rm = TRUE)
```

\
There is no association between time to eat and lunch duration for the whole smaple (r = 0.03, p = 0.172).
\
\FloatBarrier
```{r tte_plot, include=TRUE, echo=FALSE}
tte_boxplot_nooutline
```

\clearpage

# Fruit/Vegetable Selected


```{r fv_pre_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
hist(salad_bar_dat[salad_bar_dat[['fv_exclude']] == 'N', 'fv_pre'], main = 'Histogram of Selected Fruits/Vegetables, g', xlab = 'Fruit/Vegetables, g')
```

\
Total Sample Sizes: Full N = 2226, Elementary N = 630, Middle School N = 699, High School N = 897

\
\FloatBarrier

```{r fv_pre_mod, echo=FALSE, results='asis'}
kable(round(fv_served, digits = 3), "latex",  digits = 3, caption = 'Fruit/Veg Selected - Count Model', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\

Elementary Schools - Mean selected = 130.76 g (not including zeros). Each 10 more minutes spent eating (i.e., time to eat) is associated with a 5% increase in grams of F/V selected relative to mean (for those that chose F/V) - over 1 week this equates to 32 g increase of F/V selected

Overall Model, Middle and Hight Schools - Time to Eat is non-significant for grams of F/V selected (for those that chose F/V)

\
```{r fv_pre_mod_zi, echo=FALSE, results='asis'}
kable(round(fv_served_z, digits = 3), "latex",  digits = 3, caption = 'Fruit/Veg Selected - Zero Model', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
Overall Model and High Schools - For each minute less time children spent eating, there was a 4% (overall model) and 8% (high school) decrease in odds of NOT selecting F/V (i.e., longer time spent eating -> greater chance of selecting F/V)


Elementary and Middle Schools - The odds of choosing NO F/V is not significantly associated with time to eat

\
\FloatBarrier
\clearpage

# Fruit/Vegetable Consumed

```{r fv_consumed_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
hist(salad_bar_dat[salad_bar_dat[['fv_exclude']] == 'N', 'fv_consumed'], main = 'Histogram of Consumed Fruits/Vegetables, g', xlab = 'Fruit/Vegetables, g')
```

\FloatBarrier

\
Total Sample Sizes: Full N = 2226, Elementary N = 630, Middle School N = 699, High School N = 897
\

```{r fv_consumed_mod, echo=FALSE, results='asis'}
kable(round(fv_consumed, digits = 3), "latex",  digits = 3, caption = 'Fruit/Veg Consumed - Count Model', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\
Overall Model: mean consumed = 50.85 g, SD = 54.67 g. Each 10 more minutes spent eating (i.e., time to eat) is associated with a 13% increase in grams of F/V consumed relative to mean (for those that chose F/V) - over 1 week this equates to 33 g increase of F/V consumed
\

Elementary: mean consumed = 47.07 g, SD = 49.16 g. Each 10 more minutes spent eating (i.e., time to eat) is associated with a 16% increase in grams of F/V consumed relative to mean (for those that chose F/V) - over 1 week this equates to 37.5 g increase of F/V consumed
\

High Schools: mean consumed = 47.40 g, SD = 56.26 g. Each 10 more minutes spent eating (i.e., time to eat) is associated with a 8% increase in grams of F/V consumed relative to mean (for those that chose F/V) - over 1 week this equates to 19 g increase of F/V consumed
\

Middle Schools: mean consumed = 56.78 g, SD = 56.26 g. Time to Eat is non-significant for grams of F/V consumed (for those that selected some F/V)

\

```{r fv_consumed_mod_zi, echo=FALSE, results='asis'}
kable(round(fv_consumed_z, digits = 3), "latex",  digits = 3, caption = 'Fruit/Veg Consumed - Zero Model', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
High Schools - For each minute longer of time to eat, there is 5% (overall model) and 8% (high school) lower odds of consuming NO F/V

Overall Model, Elementary, and Middle Schools - The odds of consuming NO F/V is not significantly associated with time to eat

\
\FloatBarrier
\clearpage

# Fruit/Vegetable Waste

```{r fv_waste_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
hist(salad_bar_dat[salad_bar_dat[['fv_exclude']] == 'N', 'fv_post'], main = 'Histogram of Fruit/Vegetable Waste, g', xlab = 'Fruit/Vegetables, g')
```

\
Total Sample Sizes: Full N = 2226, Elementary N = 630, Middle School N = 699, High School N = 897

\
\FloatBarrier

```{r fv_waste_mod, echo=FALSE, results='asis'}
kable(round(fv_waste, digits = 3), "latex",  digits = 3, caption = 'Fruit/Veg Waste - Count Model', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

Overall Model, Elementary, Middle, and High Schools - For those that chose some F/V, time to eat is non-significant for grams of F/V wasted
\


```{r fv_waste_mod_zi, echo=FALSE, results='asis'}
kable(round(fv_waste_z, digits = 3), "latex",  digits = 3, caption = 'Fruit/Veg Waste - Zero Model', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

Overall Model, Elementary, Middle, and High Schools - The odds of wasting NO F/V is not significantly associated with time to eat

\
\FloatBarrier
\clearpage

# Fruit/Vegetable Percent Waste

```{r fv_prop_waste_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
hist(salad_bar_dat[salad_bar_dat[['fv_exclude']] == 'N', 'fv_prop_waste'], main = 'Histogram of Percent Fruits/Vegetables Waste, %', xlab = 'Fruit/Vegetables, %')
```

\
Total Sample Sizes: Full N = 2226, Elementary N = 630, Middle School N = 699, High School N = 897

\
\FloatBarrier

```{r fv_prop_waste_mod, echo=FALSE, results='asis'}
kable(round(fv_prop_waste, digits = 3), "latex",  digits = 3, caption = 'Fruit/Veg Percent Waste - Count Model', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\
Overall Model: mean percent wasted = 55.11%, Each 10 more minutes spent eating (i.e., time to eat) is associated with a decrease of 6% wasted relative to mean (for those that chose F/V) - over 1 week this equates to a decrease in percent waste of 16.5%.
\

High Schools: mean percent wasted = 49.61%, Each 10 more minutes spent eating (i.e., time to eat) is associated with a decrease of 14% waste relative to mean (for those that chose F/V) - over 1 week this equates to a decrease in percent waste of 35%.
\

Elementary, and Middle Schools - Time to eat is non-significant for grams of percent F/V waste (for those that selected F/V)

\

```{r fv_prop_waste_mod_zi, echo=FALSE, results='asis'}
kable(round(fv_prop_waste_z, digits = 3), "latex",  digits = 3, caption = 'Fruit/Veg Percent Waste - Zero Model', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\
High Schools - For each minute longer of time to eat, there is 6% greater odds of wasting ZERO percent of F/V selected (for those that selected F/V)

Overall Model, Elementary, and Middle Schools - The odds of wasting ZERO percent F/V is not significantly associated with children's time to eat

\

\FloatBarrier
\clearpage

# Supplemental Information -- Complete vs Missing Time to Eat ####

## Demographic Characteristics

```{r demo_tab_tte, echo=FALSE, results='asis'}
  as_kable_extra(overall_table_tte, caption = 'Demographic Characteristics and Variables of Interest', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage